\plaintitle

### 2016-05-25 cscw/papers/2017/labor/trackingWork.tex
first section seems mostly done; some stuff still commented out needs to be brought back in (click here to read more: the second bullet point will SHOCK you! - section 2 is getting fleshed out, and some citations are getting thrown in, but i also have this paper from ~1963 that's eerily prescient about digitally mediated gig work - section 3 is not really done, but we know we're going to make this argument about factories emerging based on the practice of establishing worker pools (something AMT affords for by letting you make hidden HITs, for example), so i think we can flesh that out soon...

% To make various LaTeX processors do the right thing with page size.
\def\pprw{8.5in}
\def\pprh{11in}
\special{papersize=\pprw,\pprh}
\setlength{\paperwidth}{\pprw}
\setlength{\paperheight}{\pprh}
\setlength{\pdfpagewidth}{\pprw}
\setlength{\pdfpageheight}{\pprh}
\definecolor{PineGreen}{HTML}{008800}
\newcommand{\msb}[1]{{\color{PineGreen}[MSB: #1]}}

@@

\section{Introduction}

% \itshape
% What am I trying to say here?
% I want to get across that researchers have looked at gig work in various ways,
% but not come up with very persuasive overarching explanations for this whole process.
% That is, there's no broader theory making sense of why all of this is happening.

% Rather than make the argument that
% these things are all independently similar to the piecework
% (something to which researchers have already made the connection),
% I want to frame this as a huge process, involving:
% \begin{enumerate}
%   \item distribution of work,
%   \textbf{which leads to\dots}
%   \item discretization and routinization of work,
%   \textbf{which allows\dots}
%   \item management (scientific \& external),
%   \textbf{which causes workers to feel\dots}
%   \item alienation from work (Marx's idea) and resistance to management (also Marx probably but a more general labor advocacy theory too)
% \end{enumerate}
% okay, let's try this:
% \upshape

The past decade has seen
microtasks, the ``sharing economy'', and other instantiations of on--demand contract work
grow to occupy the fascination of both academic circles and our culture as a whole
\cite{Ross,CrowdsourcingUserStudies,scholz2012digital}.
The research community has made connections between this emergent form of work
and the historically situated ``piecework'',
as well as a number of observations relating to
the frustration workers feel stemming from the management of this work
\cite{turkopticon,dynamo,uberAlgorithm}.
But the connections between
historical piecework and
contemporary crowd work
haven't been deeply made as yet.
% um, note to self: say more.

@@

In the reflection on the literature published in the last 5 years since
\citeauthor{crowdworkFuture}'s 
\citetitle{crowdworkFuture},
we notice a broader trend describing the change in work that's being done
% motivated by this realization,
% we look at the emergent phenomena in piecework both as interconnected
\cite{crowdworkFuture}.
Following the improvements in
breaking down tasks,
delegating work, and
managing workers more broadly,
Crowd--powered has continued to parallel historical piecework's trajectory
by outgrowing ad--hoc worker groups and coalescing into more formal working groups;
we might call this the beginning of factorization.
% "Factorization" is not the right word but I honestly have no idea what the right term is.
% The process of formalizing work into factories? Should I tweet/post/ask about this somewhere?

% Crowd work,
% they argued in \citeyear{crowdworkFuture},
% represents a threat to the future of work inasmuch as it marginalized
% and perhaps even harmed
% workers;
% their driving question, then, was
% whether the future of
% (crowd, but arguably all discretized)
% work might be one in which they wish their children to participate someday;
% it seems strikingly like one that might have been asked
% as patches of denim were first being delivered to the homes of early pieceworkers.
% % \msb{this seems speculative---I'm not sure whether they knew what was coming. and wasn't income distribution different then? Who was the `they' in this case? Industrialists?}
% agreed; i'm commenting it out for now to see how I feel without making this argument at all. If I really feel like it's missing, I should find evidence that contemporaries discussed it...

@@

This paper will attempt to demonstrate that the familiarity is more than passing;
that the phenomena researchers have observed in on--demand digitally mediated labor markets
were inevitable milestones in the birth and life of piecework.
We will set out to show that piecework itself
--- and the features inherent to it (such as decomposition of tasks) --- % and others?
precipitated the negative outcomes that historically led workers to collective organization and action in the early \nth{20} century;
that aspects of piecework like 
% Indeed, the model of work distribution and management we know as piecework
% --- including the methods and work--flows that facilitate this kind of work ---
% ultimately cause what we recognize broadly as
% frustration,
% alienation, and
% resistance
% among gig workers.

% \msb{I'd like the argue to summarize the argument as to \textbf{why} it was inevitable. Why was it inevitable then, and why is it inevitable now? What is it about piecework that generates this outcome? In two sentences or less...}
``But'',
as \citeauthor{scholz2012digital} points out,
``it would be wrong to conclude that
in the realm of digital labor there is nothing new under the sun''
\cite{scholz2012digital}.
For one, information work
(e.g. AMT \& Upwork)
and digitally managed work in general make it substantially easier
to keep workers geographically dispersed
compared to the factory workers that followed home--based piecework.
This aspect of work renders workers virtually invisible to the task solicitors
--- or ``requesters'' ---
despite being significantly more connected than historical pieceworkers were % this is a weak point...
\cite{turkopticon}.
Secondly, while
factory foremen and other middle--men
traditionally mediated the relationships between workers and managers,
today the visible agents are \textit{systems};
rather than employing individuals who ``personified the functions of management''
and can thus negotiate workers' needs,
socio--technical systems mediate these interactions % often with unrewarding outcomes
\cite{wray1949marginal}
% \cite{storiesIraniSilberman}.
Finally, this characteristic of modern piecework makes
worker coordination for collective advocacy and action significantly more difficult,
necessitating special consideration to maintain the inertia of collective will
while focusing that energy productively
\cite{dynamo}.
% here are undoubtedly more examples of differences.
% How do I not stake a claim that this is comprehensive?
% Or should I really flesh this out and make it (comprehensive)?

% Indeed, we will attempt to reason about more than the larger--scale progression from
% the discretization of work toward scientific management and future steps;
% we will attempt to make sense of how the modern processes in digital labor,
% in particular the use of the Internet as a medium to manage as well as \textit{do} work,
% affect these unfolding events.
% \msb{That felt like a bit of a calorie-free sentence --- I'm not sure what it was trying to say. I think it needs to connect the dots more visibly for the reader. Is it that we're using histories and theories of piecework to reason about that progression as it applies to today?}
% \msb{I'd like to see a 1--2 sentence summary of what the takeaways from this part of the exploration are. What is new under the sun?}

\subsection{Piecework as a lens to understand gig work}
\citeauthor{crowdworkFuture}
investigate the future of crowd work by
situating and interrogating it through ``piecework'',
\msb{I would not say that piecework was exactly the centerpiece of that paper. It was used as a point of contrast.}
a term almost lost to history \msb{a bit exaggerated}, but which for a time described
work done in the home,
in manageable tasks,
often involving clear instructions
and payment only for work completed, not work done
(the differentiation, here, being that
one would be paid for the \textit{output} of the work,
not the \textit{duration})
\cite{crowdworkFuture} \msb{is that true? by that definition, design is piecework too, right, because I get paid for the job, not for hours worked. But design doesn't seem like piecework.}.
This work was largely in textiles and was predominantly done by women,
which by itself is a topic worthy of unpacking \msb{instead of gesticulating, can we indicate what the punchline of unpacking it was?}
\cite{scott1975women}.
Given the scope, 
we'll leave this topic with the superficial takeaway that
piecework and microtasks share some structural similarities:
\msb{may be just me, but that felt like it was belittling the reader, like their puny brains wouldn't be able to understand more than a superficial takeaway}
\begin{inlinelist}
\item the work is done in the home \msb{true? isn't it still piecework if it's in a factory?};
\item the worker is paid for each discrete piece of work done, regardless of time or effort; and
\item the worker's status
(not only socially, but also economically)
is ambiguous, or at least the subject of some controversy \msb{my first reaction was ``this isn't definitional''. But now I look back and see that you're just saying there are similarities. It would be helpful if the sentence made it clearer that the similarities were in not just what the work was but also in the environment around it.}
\end{inlinelist}
It may be said that
on--demand work shares, if not inspiration \msb{I doubt it was inspiration --- `hey, let's create something like factory floors but for information work!'}, then many of the same outcomes as piecework. \msb{what are outcomes?}

\subsection{Context}
Importantly, since the reemergence of piecework we've seen substantial frustration
and resistance among the workers in this area
\cite{uberAlgorithm,turkopticon,dynamo}.
This paper attempts to make sense of the broader research on this piecework,
or ``gig work'', by framing this as one of several steps in the marginalization of workers, \msb{this feels out of order to me. I don't think resistance is a step in the marginalization of workers, isn't it a reaction to the marginalization of researchers?}
starting with the discretization of tasks,
followed by routinization and the rise of workflows,
and finally the external management of workers.
All of this is to say that these milestones follow sequentially,
not coincidentally but necessarily,
and that by tracing this path using the corpus of scholarship on labor and workers
we can both make sense of past events and perhaps reasonably predict next steps. \msb{I don't think we've offered much proof that this is the case yet. Why must they follow necessarily? Can you offer a cause and effect relationship?}

@@

\section{Case Studies}
The existing body of research has shed light on on--demand from various perspectives,
and revealed a number of topics that,
through our framing, are clearly situated together.
Those topics, at a very high level, are
\begin{enumerate}
\item the \textbf{distribution} of work,
\item the \textbf{routinization} and \textbf{discretization} of work, and finally
\item the \textbf{relationships} between the workers and the product of their work,
      as well as workers and managers.
\end{enumerate}

@@

\subsection{Distributing Work}
In both the historical and contemporary cases,
distributed, speculative work
has promised
to diffuse the costs of capital--intensive resources
(whether they were sewing machines or laboratory equipment).

@@

The insight here seems to have been that
a substantial amount of work does not necessarily need to be done in collocated space,
but can be done from one's own home or other space arranged by the worker.
Moreover, by shifting the workplace into the worker's domain,
the cost of capital involved in that work can more easily be placed on workers' backs \msb{I don't think that was the original motivation for AMT or Uber --- it was about reaching people who could not otherwise join the labor force for Amazon's data cleaning or for taxi-ing.}.
While yellow--cab organizations often manage drivers in similar ways to platforms such as Uber and Lyft
(inasmuch as drivers are often considered contractors, or otherwise exempt from the formal status of ``employee''),
these new systems go further,
by framing ownership and responsibility for costs
(e.g. automotive maintenance)
on drivers.
In our fieldwork, we discovered many longtime ``on--demand'' drivers
(affiliated with platforms such as Uber and Lyft)
who readily voiced frustration with the costs of
frequent oil changes and the unexpected replacement of expensive parts.
Distributing labor had similar effects on pieceworkers at the turn of the \nth{20} century;
textile workers were given the source material with which to work,
but were generally expected to use their own sewing materials and work in their own homes
\cite{hapke2004sweatshop}.

% the change seemed to begin with
% the redistribution of work into the homes and onto the diffuse capital of workers.
% 99designs may represent one of the first illustrative cases of
% speculative, distributed labor in the contemporary form,
% but speculative labor and even on--demand design work is not necessarily new;
% \cite{99designs}.

% distributed; uber, etc... ->
% routinization; crowdwork - > optimization
% - > accommodation and resistance, alienation?
% tom malone

% This framing of labor worked for some time in the late \nth{19} and early \nth{20} centuries,

% This work is only made to seem new by framing the units of work as the output of ``task--completion APIs'',
% making it possible
% (and indeed advantageous)
% to allocate work on the fly to people in different places
% \cite{storiesIraniSilberman}.

\subsection{Discretization and Routinization}

@@

The parallels between this kind of work and
historical piecework of the turn of the \nth{20} century
is by no means new
[\textit{citation needed --- who said this first? most notably? Turner?}] \msb{not familiar with it, but google scholar suggests this was an early one to talk about it \url{http://scholarship.law.berkeley.edu/cgi/viewcontent.cgi?article=1433&context=bjell}}.
\textit{Elaborate on gig work, piecework, etc\dots}

@@

routinization can be seen in the contemporary in workflows
\cite{foundry,bernstein2015soylent}
[\textit{There are various papers that talk about creating a workflow;
maybe this is where FFV belongs? Foundry?}].

@@

\subsection{External Management}
\textbf{Discretization}, enabling \textbf{routinization}, thus allows us to
manage work more meaningfully.
Routinization in particular made it possible
(and indeed preferable) to assume that people
% as \citeauthor{hu1961parallel} describes the premise of this sort of work,
``\dots are of equal ability and \dots can do any of the $n$ jobs''
\cite{hu1961parallel}.
\citeauthor{storiesIraniSilberman}
find similarly that
this work is only made to seem new by framing the units of work as the output of ``task--completion APIs''
% making it possible
% (and indeed advantageous)
% to allocate work on the fly to people in different places
\cite{storiesIraniSilberman}.

Crucially,
\citeauthor{hu1961parallel}'s case study assumed that workers were similarly trained and capable,
which in \citeyear{hu1961parallel}
meant that workers would at least have to be trained in person, if not instructed as well.
Throughout the industrial revolution, workers flocked to centralized locales of production,
and physically situated factories made it both
difficult to ignore the general pattern of mistreatment and
relatively easy to organize.

% construction and manufacturing in various forms
% (from textiles to automobiles)
% encourage the consolidation of capital--intensive resources like factories.
% The prohibitively expensive nature of factory equipment may have been a key factor in 
\citeauthor{storiesIraniSilberman} describe is that the ``APIs'' in the latter case

% evaluate work in abstraction.
% This means that we can

\textit{I want to cite Justin's work on crowdsourcing effort to highlight that
we can evaluate workers for the work they do with increasingly finite amounts of time;
also, Ranjay's work that embraces failure because
we can essentially algorithmically make sense of failure (let's call it noise)
and re--capture signal.}

\subsection{Resistance}
So it's not surprising, then, that workers are frustrated:
Turkopticon, Dynamo, and many other pieces of work point this out
\cite{turkopticon,dynamo,uberAlgorithm}
[\textit{also want to cite Brian's work from CHI this year}].
In popular culture, reporters have inquired about
what ``the future of labor unions'' will look like
[\textit{Imagine I had cited an online article and
it wasn't totally inappropriate for a conference}].

\textit{The parallels here would be difficult to ignore;
Lily and others have pointed this out,
but it's worth thinking about the broader trend of
resisting management,
driven by routinization,
enabled by discretization.
Do that here.}

>>>>

% To make various LaTeX processors do the right thing with page size.
\def\pprw{8.5in}
\def\pprh{11in}
\special{papersize=\pprw,\pprh}
\setlength{\paperwidth}{\pprw}
\setlength{\paperheight}{\pprh}
\setlength{\pdfpagewidth}{\pprw}
\setlength{\pdfpageheight}{\pprh}
\definecolor{PineGreen}{HTML}{008800}
\definecolor{BrickRed}{HTML}{FF0000}
\newcommand{\msb}[1]{{\color{PineGreen}[MSB: #1]}}
\newcommand{\ali}[1]{{\color{BrickRed}[\textit{al2: #1}]}}

@@

\section{Introduction}
The past decade has seen
microtasks, the ``sharing economy'', and other instantiations of on--demand contract work
grow to occupy the fascination of both academic circles and our culture as a whole
\cite{Ross,CrowdsourcingUserStudies,scholz2012digital}.
The research community has made connections between this emergent form of work
and the historically situated ``piecework'',
as well as a number of observations relating to
the frustration workers feel stemming from the management of this work
\cite{turkopticon,dynamo,uberAlgorithm}.
But the connections between
historical piecework and
contemporary crowd work
haven't been deeply made as yet.
% um, note to self: say more.

@@

In the reflection on the literature published in the last 5 years since
\citeauthor{crowdworkFuture}'s 
\citetitle{crowdworkFuture},
we notice a broader trend describing the change in work that's being done
\cite{crowdworkFuture}.
Following the improvements in
breaking down tasks,
delegating work, and
managing workers more broadly,
Crowd--powered has continued to parallel historical piecework's trajectory
by outgrowing ad--hoc worker groups and coalescing into more formal working groups;
we might call this the beginning of factorization.
% "Factorization" is not the right word but I honestly have no idea what the right term is.
% The process of formalizing work into factories? Should I tweet/post/ask about this somewhere?

% Crowd work,
% they argued in \citeyear{crowdworkFuture},
% represents a threat to the future of work inasmuch as it marginalized
% and perhaps even harmed
% workers;
% their driving question, then, was
% whether the future of
% (crowd, but arguably all discretized)
% work might be one in which they wish their children to participate someday;
% it seems strikingly like one that might have been asked
% as patches of denim were first being delivered to the homes of early pieceworkers.
% agreed; i'm commenting it out for now to see how I feel without making this argument at all. If I really feel like it's missing, I should find evidence that contemporaries discussed it...

@@

This paper will attempt to demonstrate that the familiarity is more than passing;
that the phenomena researchers have observed in on--demand digitally mediated labor markets
were inevitable milestones in the birth and life of piecework.
We will set out to show that this perspective of crowd work as an embodiment of piecework
predicts the myriad outcomes of contemporary crowd work, including
our developments of work--flows further abstracting work,
the troubling effects of those developments on factors such as pay and work quality, and
many if not all of the frustrations researchers have discovered among workers
in the study of crowd and gig work.

``But'',
as \citeauthor{scholz2012digital} points out,
``it would be wrong to conclude that
in the realm of digital labor there is nothing new under the sun''
\cite{scholz2012digital}.
For one, information work
(e.g. AMT \& Upwork)
and digitally managed work in general make it substantially easier
to keep workers geographically dispersed
compared to the factory workers that followed home--based piecework.
This aspect of work renders workers virtually invisible to the task solicitors
--- or ``requesters'' ---
despite being significantly more connected than historical pieceworkers were % this is a weak point...
\cite{turkopticon}.
Secondly, while
factory foremen and other middle--men
traditionally mediated the relationships between workers and managers,
today the visible agents are \textit{systems};
rather than employing individuals who ``personified the functions of management''
and can thus negotiate workers' needs,
socio--technical systems mediate these interactions % often with unrewarding outcomes
\cite{wray1949marginal}.
% \cite{storiesIraniSilberman}.
Finally, this characteristic of modern piecework makes
worker coordination for collective advocacy and action significantly more difficult,
necessitating special consideration to maintain the inertia of collective will
while focusing that energy productively
\cite{dynamo}.
\ali{I really don't like this paragraph\dots}
% here are undoubtedly more examples of differences.
% How do I not stake a claim that this is comprehensive?
% Or should I really flesh this out and make it (comprehensive)?

\subsection{Piecework as a lens to understand gig work}
\citeauthor{crowdworkFuture}
investigate the future of crowd work by
situating and interrogating it through ``piecework'',
which historically described work done in the home,
in manageable tasks,
often involving clear instructions
and payment only for work completed, not work done
(the differentiation, here, being that
one would be paid for the \textit{output} of the work,
not the \textit{duration})
\cite{crowdworkFuture}.
% \msb{is that true? by that definition, design is piecework too, right, because I get paid for the job, not for hours worked. But design doesn't seem like piecework.}.
% This work was largely in textiles and was predominantly done by women,
% which by itself is a topic worthy of unpacking
% \msb{instead of gesticulating, can we indicate what the punchline of unpacking it was?}
% \ali{let's just leave this in the graveyard for now; i feel like someone who knows what they're talking about with regard to feminist and gender studies
% (e.g. the Bardzells, Irani) would really do justice here, but i'd be getting in over my head}
% \cite{scott1975women}.
Given the scope,
we can frame piecework and gig work as sharing these important similarities:
\begin{inlinelist}
\item this form of work began in the home
\item the worker is paid for each discrete piece of work done, regardless of time or effort; and
\item the worker's status
(not only socially, but also economically)
is ambiguous, or at least the subject of some controversy.
% \msb{my first reaction was ``this isn't definitional''. But now I look back and see that you're just saying there are similarities. It would be helpful if the sentence made it clearer that the similarities were in not just what the work was but also in the environment around it.}
\end{inlinelist}.

\subsection{Context}
Importantly, since the reemergence of piecework we've seen substantial frustration
and resistance among the workers in this area
\cite{uberAlgorithm,turkopticon,dynamo}.
This paper attempts to make sense of the broader research on this piecework,
or ``gig work'', by framing this as one of several steps in the marginalization of workers,
% \msb{this feels out of order to me. I don't think resistance is a step in the marginalization of workers, isn't it a reaction to the marginalization of researchers?}
%
% this needs to be re-written to reflect the new split
%
%
% starting with the discretization of tasks,
% followed by routinization and the rise of work--flows,
% and finally the external management of workers.
% 
All of this is to say that these milestones follow sequentially,
not coincidentally but necessarily,
and that by tracing this path using the corpus of scholarship on labor and workers
we can both make sense of past events and perhaps reasonably predict next steps.
% \msb{I don't think we've offered much proof that this is the case yet. Why must they follow necessarily? Can you offer a cause and effect relationship?}

@@

\section{Case Studies}
The existing body of research has shed light on on--demand from various perspectives,
and revealed a number of topics that,
through our framing, are clearly situated together.
Those topics are, at a high level, as follows:
\begin{enumerate}
\item the processes involved in making work into tasks, or \textbf{discretization},
in ``\nameref{sec:MakingGigsWork}'';
\item the outcomes of that discretization, both on the work itself as well as the workers,
in ``\nameref{sec:Fallout}'';
and finally
\item the results of these forces; namely the turning of work toward \textbf{factories},
which we will discuss in ``\dots''.
\end{enumerate}

@@

\subsection{Making Gig(s) Work}\label{sec:MakingGigsWork}
% this is phase 1: the decomposition & abstraction of work;
% all of the research that has gone into work--flows and
% all the things we can do with crowd work.

In this section, we'll consider several components of contemporary piecework
that relate to its historical parallel.
In particular, we'll look at the ``decomposition'' of complex skill--intensive tasks
into smaller, more abstracted work, as well as the routinization that this allows.

In both the historical and contemporary cases,
distributed, speculative work
has promised
to diffuse the costs of capital--intensive resources
(whether they were sewing machines or laboratory equipment).

@@

% The insight here seems to have been that
% a substantial amount of work does not necessarily need to be done in collocated space,
% but can be done from one's own home or other space arranged by the worker.
% Moreover, by shifting the workplace into the worker's domain,
% the cost of capital involved in that work can more easily be placed on workers' backs
% \msb{I don't think that was the original motivation for AMT or Uber --- it was about reaching people who could not otherwise join the labor force for Amazon's data cleaning or for taxi-ing.}.
% I didn't mean that this was some insight that Uber or Lyft had, but that this was some part of what makes Uber work;
% i would argue categorically that these companies wouldn't functionally work if they weren't able to obviate the 
% maintenance costs that a factory owner would associate with their capital (e.g. auto costs)
While yellow--cab organizations often manage drivers in similar ways to platforms such as Uber and Lyft
(inasmuch as drivers are often considered contractors, or otherwise exempt from the formal status of ``employee''),
these new systems go further
by framing ownership and responsibility for costs
(e.g. automotive maintenance)
on drivers.
In our fieldwork, we discovered many longtime ``on--demand'' drivers
(affiliated with platforms such as Uber and Lyft)
who readily voiced frustration with the costs of
frequent oil changes and the unexpected replacement of expensive parts.
Distributing labor had similar effects on pieceworkers at the turn of the \nth{20} century;
textile workers were given the source material with which to work,
but were generally expected to use their own sewing materials and work in their own homes
\cite{hapke2004sweatshop}.

% \subsection{Discretization and Routinization}

@@

The parallels between this kind of work and
historical piecework of the turn of the \nth{20} century
is by no means new.
% [\textit{citation needed --- who said this first? most notably? Turner?}] \msb{not familiar with it, but google scholar suggests this was an early one to talk about it \url{http://scholarship.law.berkeley.edu/cgi/viewcontent.cgi?article=1433&context=bjell}}.
% \textit{Elaborate on gig work, piecework, etc\dots}

@@

routinization can be seen in the contemporary in work--flows
\cite{foundry,bernstein2015soylent}.
% [\textit{There are various papers that talk about creating a work--flow;
% maybe this is where FFV belongs? Foundry?}].

@@

\subsection{The Fallout of Gig Work}\label{sec:Fallout}
If the research exploring and documenting how we can exploit crowd \textit{work} can be described as wide--ranging,
the scholarship discussing the ways crowd \textit{workers} have been exploited is more focused;
\citeauthor{turkopticon} point out the disillusion that companies such as Amazon foster on platforms for work like AMT
(see also \citeauthor{dynamo}'s work
continuing in the spirit of this observation to generate collective action to improve worker conditions)
\cite{turkopticon,dynamo}.
\citeauthor{uberAlgorithm}
find similarly that workers on gig work platforms are frustrated by the systems on which they work,
to say little of the policies which these systems enforce
\cite{uberAlgorithm}.

\itshape
sections here should include:
\begin{enumerate}
\item ``flexibility'' \cite{friedman2014workers,DesigningForLabourUber}
\item leads to ``low pay'' \cite{turkopticon,dynamo}
\item leads to ``variable quality work''
\end{enumerate}

\upshape

\subsection{Factories}

% I commented everything going forward out not because it's all trash (it's not!)
% but because we pretty significantly reframed the cases to be studying and
% i didn't want the structure from before to influence the rewrite;
% we should be bringing content from below back above. just, judiciously...

% \subsection{Discretization and Routinization}

% Distributing work in method described above may be thought of as vertically slicing work such that 
% each person is responsible for the whole task
% --- making a whole garment or being responsible for driving in a single neighborhood.
% Broken down in this way, work could grow to unprecedented scales,
% but the quality of the work would remain relatively variable.
% Textile work being a salient example,
% some seamstresses might be better than others at the same task,
% making this framing of the work initially problematic.

% A compelling solution emerged in the early \nth{20} century to break tasks down into discrete,
% manageable routines that could be taught relatively easily,
% and whose work output could be evaluated in abstraction from the rest of the work.
% In Ford's assembly line, this meant that workers were not responsible for building a whole car,
% but a single very narrowly defined action that needed to be done on every car.

% This approach paralleled what would be known as ``Taylorism'',
% and its influences can be seen today in crowd work and micro--tasks.
% \textit{talk about breaking tasks down both in general (Cheng) and even for the self (Teevan);
% horizontal cuts instead of vertical}
% \cite{cheng2015break,writingMicroTasks}.
% By decomposing and recomposing tasks,
% and in particular by assigning similarly natured work to the same workers,
% workers could become ``experts'' in a small aspect of the work that they did,
% speeding their work dramatically
% \cite{delayAndOrderLasecki}.
% Perhaps more important, however, was that
% the breaking down of work into tasks has made it more practical to evaluate work at each stage
% [\textit{citation needed}].

% Opening the door to more discrete modules of work known as tasks 
% Contributions such as
% ``find--fix--verify'' % (described in \citetitle{bernstein2015soylent})
% and
% ``Cascade'' % (described in \citetitle{chilton2013cascade})
% make it easier to assign smaller components of work to myriad workers and
% recompose the constituent parts into something more complex
% \cite{bernstein2015soylent,chilton2013cascade}.
% Some work has taken special interest in the process of breaking tasks down into more manageable parts
% inasmuch as decomposing what we might call ``macro'' tasks into microtasks,
% both for the purposes of crowd--sourcing in the sense of out--sourcing work
% as well as ``selfsourcing''
% \cite{cheng2015break,teevan2014selfsourcing}.

% The parallels between this kind of work and
% historical piecework of the turn of the \nth{20} century
% is by no means new
% [\textit{citation needed --- who said this first? most notably? Turner?}] \msb{not familiar with it, but google scholar suggests this was an early one to talk about it \url{http://scholarship.law.berkeley.edu/cgi/viewcontent.cgi?article=1433&context=bjell}}.
% \textit{Elaborate on gig work, piecework, etc\dots}

% The \textbf{discretization} and decomposition of work certainly facilitates
% breaking tasks down,
% parallelizing work,
% and getting more done across a broader array of people;
% but the key advantage in turning macro tasks 
% into many micro tasks is that we can make that work \textit{routine}.

% By making larger bodies of work less contextually situated,
% we can define processes that make that work
% and the instructions thereof
% useful for virtually anyone with shared cultural or intellectual background.

% routinization can be seen in the contemporary in work--flows
% \cite{foundry,bernstein2015soylent}
% [\textit{There are various papers that talk about creating a work--flow;
% maybe this is where FFV belongs? Foundry?}].

% \subsection{External Management}
% \textbf{Discretization}, enabling \textbf{routinization}, thus allows us to
% manage work more meaningfully.
% Routinization in particular made it possible
% (and indeed preferable) to assume that people
% ``\dots are of equal ability and \dots can do any of the $n$ jobs''
% \cite{hu1961parallel}.
% \citeauthor{storiesIraniSilberman}
% find similarly that
% this work is only made to seem new by framing the units of work as the output of ``task--completion APIs''
% \cite{storiesIraniSilberman}.

% Crucially,
% \citeauthor{hu1961parallel}'s case study assumed that workers were similarly trained and capable,
% which in \citeyear{hu1961parallel}
% meant that workers would at least have to be trained in person, if not instructed as well.
% Throughout the industrial revolution, workers flocked to centralized locales of production,
% and physically situated factories made it both
% difficult to ignore the general pattern of mistreatment and
% relatively easy to organize.

% \citeauthor{storiesIraniSilberman} describe is that the ``APIs'' in the latter case

% \textit{I want to cite Justin's work on crowdsourcing effort to highlight that
% we can evaluate workers for the work they do with increasingly finite amounts of time;
% also, Ranjay's work that embraces failure because
% we can essentially algorithmically make sense of failure (let's call it noise)
% and re--capture signal.}

% \subsection{Resistance}
% So it's not surprising, then, that workers are frustrated:
% Turkopticon, Dynamo, and many other pieces of work point this out
% \cite{turkopticon,dynamo,uberAlgorithm}
% [\textit{also want to cite Brian's work from CHI this year}].
% In popular culture, reporters have inquired about
% what ``the future of labor unions'' will look like
% [\textit{Imagine I had cited an online article and
% it wasn't totally inappropriate for a conference}].

% \textit{The parallels here would be difficult to ignore;
% Lily and others have pointed this out,
% but it's worth thinking about the broader trend of
% resisting management,
% driven by routinization,
% enabled by discretization.
% Do that here.}
